Data preparation

### 2024-02-01 procesamiento/01-prod_prep-micro.Rmd
up

df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
# View(df1[,c("homclass","homclass_gc")])
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf

@@

df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
sjlabelled::set_label(df1$homclass3) <- "Class homogeneity"
df1$homclass3_gc <- group_center(x = df1$homclass3,grp = df1$country)
# View(df1[,c("homclass","homclass_gc")])
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf

>>>>

df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
df1$homclass2 <- as.numeric(df1$ingroup/df1$know_total)
sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (isko - v2)"
df1$homclass2_gc <- group_center(x = df1$homclass2,grp = df1$country)
# View(df1[,c("homclass","homclass_gc")])
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf

@@

df1 %>% select(dclass3,n_high,n_middle,n_low,outgroup,ingroup,eindex)
df1$homclass3 <- as.numeric(df1$ingroup/df1$know_total)
sjlabelled::set_label(df1$homclass3) <- "Class homogeneity (DIGCLASS version)"
df1$homclass3_gc <- group_center(x = df1$homclass3,grp = df1$country)
# View(df1[,c("homclass","homclass_gc")])
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf
